Face Attractiveness and the Sense of Reality

### 2022-09-12 analysis.Rmd
update

df <- read.csv("data/data.csv") |>
  mutate(
    Date = lubridate::dmy(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    # Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other"),
    Belief = fct_relevel(Belief, "Fake", "Real"),
    Stimulus_Interest = case_when(
      Sexual_Orientation == "Heterosexual" & Stimulus_SameSex == "Opposite" ~ TRUE,
      Sexual_Orientation == "Heterosexual" & Stimulus_SameSex == "Same" ~ FALSE,
      Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Opposite" ~ FALSE,
      Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Same" ~ TRUE,
      Sexual_Orientation == "Bisexual" ~ TRUE,
      TRUE ~ NA
    )
  )

@@

# Create individual scores for Simulation Monitoring
df <- df |>
  group_by(Participant, Belief) |>
  summarise(Confidence = mean(abs(Belief_Confidence)),
            n = n() / 109) |> 
  pivot_wider(names_from = "Belief", values_from = c("Confidence", "n")) |>
  ungroup() |> 
  merge(df, by = "Participant")
```

@@

```{r message=FALSE, warning=FALSE}
outliers <- c(
  # Very short duration for questionnaire in particular + low rating correlations
  "5eaef8702b68455d6e130595_ptsga"
  )
outliers_partial <- c(
  "5c6414540821d30001046198_x9q7r",
  "60dd7b03f1e72d38230df476_9yh9n")
```

@@

@@

```{r message=FALSE, warning=FALSE}
dfsub$r_Trustworthy <- NA
dfsub$r_Attractive <- NA
dfsub$r_Goodlooking <- NA
for (participant in dfsub$Participant) {
  dfsub[dfsub$Participant == participant, "r_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
  dfsub[dfsub$Participant == participant, "r_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
  dfsub[dfsub$Participant == participant, "r_Goodlooking"] <- cor(df[df$Participant == participant, "Goodlooking"], df[df$Participant == participant, "Norms_Attractive"])
}
```

@@

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  mutate(Attention_Check = paste0(
    insight::format_value(Attention_Check, 1),
    " (", insight::format_value(Attention_Check1, 1),
    ", ",
    insight::format_value(Attention_Check2, 1),
    ", ",
    insight::format_value(Attention_Check3, 1),
    ")"
  )) |>
  select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |>
  datawizard::data_relocate("Attention_Check", 2) |>
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |> 
  kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")
```

@@

p_cor <- dfsub |>
  select(Participant, starts_with("r_")) |>
  pivot_longer(-Participant) |>
  mutate(name = str_remove(name, "r_")) |>
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
  scale_color_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
  see::theme_modern() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, 
                               color = ifelse(levels(dfsub$Participant) %in% outliers, "red", ifelse(levels(dfsub$Participant) %in% outliers_partial, "orange", "black"))),
    legend.position = "top"
  ) +
  labs(y = "Correlation", fill = "") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

@@

p5 <- plot_waffle(dfsub, "Nationality") +
  scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "Eastern" = "#673AB7", "African" = "#4CAF50", "South African" = "#009688"))

@@

patchwork::wrap_plots(list(p1, p2, p3, p4, p5, p6, p7, p8))
```

@@

```{r message=FALSE, warning=FALSE}
# plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))

df |>
  mutate(Participant = fct_relevel(Participant, df |> 
    group_by(Participant) |>
    summarize(Belief_Answer = mean(Belief_Answer)) |>
    ungroup() |>
    arrange(Belief_Answer) |>
    pull(Participant) |>
    as.character())) |>
  # mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |>
  ggplot(aes(x = Belief_Answer, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(0.5, 0.5)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0, 0),
    breaks = c(-1, 0, 1),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

```{r message=FALSE, warning=FALSE}
IVs <- c("Attractive", "Goodlooking", "Trustworthy", "Familiar")

preds <- data.frame()
dats <- data.frame()
for (x in IVs) {
  for (y in IVs) {
    if (x == y) next
    print(paste(y, "~", x))
    model <- glmmTMB::glmmTMB(as.formula(
      paste(y, "~", x, "* Sex * Stimulus_SameSex + (1|Participant) + (1|Stimulus)")
    ),
    data = df,
    family = glmmTMB::beta_family()
    )

@@

    pred <- estimate_relation(model, at = c(x, "Stimulus_SameSex", "Sex"), length = 20)
    pred$y <- y
    pred <- data_rename(pred, x, "Score")
    pred$x <- x
    preds <- rbind(preds, pred)

    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x = x, y = y))
  }
}

@@

```{r message=FALSE, warning=FALSE}
dats |>
  ggplot(aes(x = Score, y = Predicted)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  # geom_ribbon(data = preds, aes(ymin = CI_low, ymax = CI_high, group = Stimulus_SameSex), alpha = 0.3) +
  geom_line(data = preds, aes(color = Sex, linetype=Stimulus_SameSex)) +
  scale_fill_gradientn(colors = c("white", "#FF9800", "#F44336"), guide = "none") +
  scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  facet_grid(y ~ x, switch = "both") +
  theme_modern() +
  labs(title = "Collinearity in the Stimuli Ratings") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "grey", color = "white") +
  ggside::geom_ysidedensity(fill = "grey", color = "white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Belief ~ poly(Delay, 2) + (1|Participant) + (1|Stimulus),
      data = df,
      family = "binomial"
    )
pred <- estimate_relation(model, at = "Delay", length = 20)

m_conf <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief / poly(Delay, 2) + (1|Participant) + (1|Stimulus),
      data = df,
      family = glmmTMB::beta_family()
    )
y_conf <- estimate_relation(m_conf, at = c("Delay", "Belief"), length = 20)
y_conf <- y_conf |> 
  mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range=c(0, 1), to=c(0.5, 1)), datawizard::rescale(x, range=c(1, 0), to=c(0, 0.5))))

df |>
  ggplot(aes(x = Delay, y = Real)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data=y_conf, aes(y=Predicted, group=Belief), linetype = "dashed") +
  geom_ribbon(data=pred, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data=pred, aes(y=Predicted), color="red") +
  scale_fill_gradientn(colors = c("white", "#795548"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_modern() +
  labs(title = "Effect of Re-exposure Delay", x = "Minutes") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "#795548", color = "white") +
  ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

@@

```{r message=FALSE, warning=FALSE}
make_model <- function(df, var = "Attractive", formula=var, fill = "#2196F3") {
  m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", formula)),
                             data = df,
                             family = "binomial")
  y_real <- estimate_relation(m_real, at = c(var, "Sex"), length = 20)

  m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief /", formula)),
        data = df,
        family = glmmTMB::beta_family()
      )
  y_conf <- estimate_relation(m_conf, at = c(var, "Belief", "Sex"), length = 20)
  y_conf <- y_conf |> 
    mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range=c(0, 1), to=c(0.5, 1)), datawizard::rescale(x, range=c(1, 0), to=c(0, 0.5))))

  p <- df |>
    ggplot(aes_string(x = var, y = "Real")) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
    scale_fill_gradientn(colors = c("white", fill), guide = "none") +
    ggnewscale::new_scale_fill() +
    geom_hline(yintercept = 0.5, linetype = "dotted") +
    # geom_point2(alpha = 0.25, size = 4, color = "black") +
    geom_line(data=y_conf, aes(y=Predicted, group=interaction(Belief, Sex), color=Sex), linetype="dashed") +
    geom_ribbon(data = y_real, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
    geom_line(data = y_real, aes(y = Predicted, color=Sex)) +

    scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_fill_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
    scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
    theme_modern(axis.title.space=0) + 
    ggside::geom_xsidedensity(fill = fill, color = "white") +
    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))

  list(p=p)
}
```

```{r message=FALSE, warning=FALSE}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Attractive, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
                     var="Attractive", fill = "#F44336")
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Goodlooking, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
                     var="Goodlooking", fill = "#E91E63")
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Trustworthy, 2) * Sex + Goodlooking + (1|Participant) + (1|Stimulus)", 
                     var="Trustworthy", fill = "#4CAF50")
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE), 
                     formula = "poly(Familiar, 2) * Sex + (1|Participant) + (1|Stimulus)", 
                     var="Familiar", fill = "#2196F3")

(rez_at$p +
  theme(axis.text.x = element_blank()) +
  labs(x = "Attractiveness") |
rez_gl$p +
  labs(x = "Beauty") +
  theme(axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
) / 
(rez_tr$p +
  labs(x = "Trustworthiness") |
rez_fa$p +
  labs(x = "Familiarity") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())
) + 
  plot_annotation(title = "Determinants of Reality Beliefs", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5))) +
  plot_layout(guides = "collect")
```

>>>>

df <- read.csv("data/data.csv") |>
  mutate(
    Date = lubridate::dmy(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other", "Prefer not to Say"),
    Belief = fct_relevel(Belief, "Fake", "Real"),
    Stimulus_Interest = case_when(
      Sexual_Orientation == "Heterosexual" & Stimulus_SameSex == "Opposite" ~ TRUE,
      Sexual_Orientation == "Heterosexual" & Stimulus_SameSex == "Same" ~ FALSE,
      Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Opposite" ~ FALSE,
      Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Same" ~ TRUE,
      Sexual_Orientation %in% c("Bisexual", "Queer") ~ TRUE,
      TRUE ~ NA
    )
  )

@@

# Create individual scores for Simulation Monitoring
df <- df |>
  group_by(Participant, Belief) |>
  summarise(
    Confidence = mean(abs(Belief_Confidence)),
    n = n() / 109
  ) |>
  pivot_wider(names_from = "Belief", values_from = c("Confidence", "n")) |>
  ungroup() |>
  merge(df, by = "Participant")
```

@@

```{r message=FALSE, warning=FALSE}
outliers <- c(
  # Very short duration for questionnaire in particular + low rating correlations
  "5eaef8702b68455d6e130595_ptsga",
  "5f0f0a2a8b2a480447f31b21_lqgpz",
  "611d03b822d4c8e041ea0c32_m0knb"
)
outliers_partial <- c(
  "5dc3485219ca0326027ce91f_37ho9",
  "5c6414540821d30001046198_x9q7r",
  "60dd7b03f1e72d38230df476_9yh9n",
  "5962799cb752840001ca478b_jh4sl",
  "5f44c23fbf2ddb80bcdf0edc_dnbny",
  "5e80370d48b5f47170e30e5c_5w2gf"
)
```

@@

### Extreme Items

```{r message=FALSE, warning=FALSE}
extreme_items <- df |>
  group_by(Stimulus, Belief) |>
  summarize(n = n() / length(unique(df$Participant))) |>
  pivot_wider(values_from = "n", names_from = "Belief") |>
  mutate(File = paste0("experiment/stimuli/AMFD/", Stimulus)) |>
  arrange(Real) |>
  filter(Real < 0.15 | Real > 0.85)

p_item <- df |>
  filter(Stimulus %in% extreme_items$Stimulus) |>
  mutate(Stimulus = fct_relevel(Stimulus, as.character(extreme_items$Stimulus))) |>
  ggplot(aes(x = Belief_Answer, y = Stimulus, fill = Stimulus)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  ggimage::geom_image(data = extreme_items, aes(image = File, x = 0, y = Stimulus), size = 0.1, by = "height") +
  # scale_y_discrete(expand = c(0.5, 0.5)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0, 0),
    breaks = c(-1, 0, 1),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d(option = "inferno") +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
# p_item

df <- df |>
  filter(!Stimulus %in% extreme_items$Stimulus)
```

We removed `r nrow(extreme_items)` trials per participant.

@@

```{r message=FALSE, warning=FALSE}
dfsub$r_Trustworthy <- NA
dfsub$r_Attractive <- NA
dfsub$r_Beauty <- NA
for (participant in dfsub$Participant) {
  dfsub[dfsub$Participant == participant, "r_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
  dfsub[dfsub$Participant == participant, "r_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
  dfsub[dfsub$Participant == participant, "r_Beauty"] <- cor(df[df$Participant == participant, "Beauty"], df[df$Participant == participant, "Norms_Attractive"])
}
```

@@

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c(paste0("Total (n=", nrow(dfsub), ")")), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  mutate(Attention_Check = paste0(
    insight::format_value(Attention_Check, 1),
    " (", insight::format_value(Attention_Check1, 1),
    ", ",
    insight::format_value(Attention_Check2, 1),
    ", ",
    insight::format_value(Attention_Check3, 1),
    ")"
  )) |>
  select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |>
  datawizard::data_relocate("Attention_Check", 2) |>
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")
# kableExtra::row_spec(which(str_detect(dfsub$Participant, "613a972033d79df11a6570de")) + 1, background = "green")
```

@@

p_cor <- dfsub |>
  select(Participant, starts_with("r_")) |>
  pivot_longer(-Participant) |>
  mutate(name = str_remove(name, "r_")) |>
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
  scale_color_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
  see::theme_modern() +
  theme(
    axis.text.x = element_text(
      angle = 45, hjust = 1,
      color = ifelse(levels(dfsub$Participant) %in% outliers, "red", ifelse(levels(dfsub$Participant) %in% outliers_partial, "orange", "black"))
    ),
    legend.position = "top"
  ) +
  labs(y = "Correlation", fill = "") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

@@

p5 <- dfsub |>
  group_by(Nationality) |>
  mutate(n = n()) |>
  ungroup() |>
  mutate(Nationality = fct_reorder(Nationality, desc(n))) |>
  ggplot(aes(Nationality)) +
  geom_bar(aes(fill = Nationality)) +
  scale_fill_viridis_d(guide = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

patchwork::wrap_plots(list(p1, p2, p3, p4, p5, p6, p8))
```

@@

```{r message=FALSE, warning=FALSE, fig.height=fig.width*1.5}
# plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))
df |>
  mutate(Participant = fct_relevel(Participant, df |>
    group_by(Participant) |>
    summarize(Belief_Answer = mean(Belief_Answer)) |>
    ungroup() |>
    arrange(Belief_Answer) |>
    pull(Participant) |>
    as.character())) |>
  # mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |>
  ggplot(aes(x = Belief_Answer, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups", color = "black", size = 0.1) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(0.02, 0)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0, 0),
    breaks = c(-0.95, 0, 0.95),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "grey", color = "white") +
  ggside::scale_xsidey_continuous(expand = c(0, 0))
```

@@

```{r message=FALSE, warning=FALSE}
IVs <- c("Attractive", "Beauty", "Trustworthy", "Familiar")

preds <- data.frame()
dats <- data.frame()
for (x in IVs) {
  for (y in IVs) {
    if (x == y) next
    print(paste(y, "~", x))
    model <- glmmTMB::glmmTMB(as.formula(
      paste(y, "~", x, "* Sex * Stimulus_Interest + (1|Participant) + (1|Stimulus)")
    ),
    data = df,
    family = glmmTMB::beta_family()
    )

@@

    pred <- estimate_relation(model, at = c(x, "Stimulus_Interest", "Sex"), length = 20)
    pred$y <- y
    pred <- data_rename(pred, x, "Score")
    pred$x <- x
    preds <- rbind(preds, pred)

    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x = x, y = y, Sex = df$Sex))
  }
}

@@

```{r message=FALSE, warning=FALSE}
dats |>
  ggplot(aes(x = Score, y = Predicted)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  # geom_ribbon(data = preds, aes(ymin = CI_low, ymax = CI_high, group = Stimulus_SameSex), alpha = 0.3) +
  geom_line(data = preds, aes(color = Sex, linetype = Stimulus_Interest)) +
  scale_fill_gradientn(colors = c("white", "#FF9800", "#F44336"), guide = "none") +
  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
  scale_linetype_manual(values = c("TRUE" = "solid", "FALSE" = "dashed")) +
  scale_x_continuous(expand = c(0, 0), labels = scales::percent()) +
  scale_y_continuous(expand = c(0, 0), labels = scales::percent()) +
  facet_grid(y ~ x, switch = "both") +
  theme_modern() +
  labs(title = "Collinearity in the Stimuli Ratings") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggnewscale::new_scale_fill() +
  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
  ggside::geom_xsidedensity(aes(fill = Sex), color = NA, alpha = 0.3) +
  ggside::geom_ysidedensity(aes(fill = Sex), color = NA, alpha = 0.3) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Belief ~ Delay + (1 | Participant) + (1 | Stimulus),
  data = df,
  family = "binomial"
)
pred <- estimate_relation(model, at = "Delay", length = 20)

m_conf <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief / Delay + ((Belief / Delay) | Participant) + (1 | Stimulus),
  data = df,
  family = glmmTMB::beta_family()
)
y_conf <- estimate_relation(m_conf, at = c("Delay", "Belief"), length = 20)
y_conf <- y_conf |>
  mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range = c(0, 1), to = c(0.5, 1)), datawizard::rescale(x, range = c(1, 0), to = c(0, 0.5))))

df |>
  ggplot(aes(x = Delay, y = Real)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data = y_conf, aes(y = Predicted, group = Belief), linetype = "dashed", color = "red") +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_line(data = pred, aes(y = Predicted), color = "red") +
  scale_fill_gradientn(colors = c("white", "#795548"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
  theme_modern() +
  labs(title = "Effect of Re-exposure Delay", x = "Minutes") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "#795548", color = "white") +
  ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")

parameters::parameters(model)
```

@@

```{r message=FALSE, warning=FALSE}
make_model <- function(df, var = "Attractive", formula = var, fill = "#2196F3") {
  # Models
  m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", formula)),
    data = df,
    family = "binomial"
  )
  y_real <- estimate_relation(m_real, at = c(var, "Sex"), length = 21)
  # gam <- brms::brm(paste0("Belief ~ s(", var, ", by=Sex) + (1|Participant) + (1|Stimulus)"),
  #                  data=df,
  #                  algorithm="sampling",
  #                  family = "bernoulli")
  # trend <- estimate_relation(gam, at = c(var, "Sex"), length = 81, preserve_range=FALSE)
  # slope <- estimate_slopes(gam, trend=var, at = c(var, "Sex"), length = 81)
  # trend$Trend <- interpret_pd(slope$pd)
  # trend$group <- 0
  # trend$group[2:nrow(trend)] <- as.character(cumsum(ifelse(trend$Trend[2:nrow(trend)] == trend$Trend[1:nrow(trend)-1], 0, 1)))

  m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief /", formula)),
    data = df,
    family = glmmTMB::beta_family()
  )
  y_conf <- estimate_relation(m_conf, at = c(var, "Belief", "Sex"), length = 21)
  y_conf <- y_conf |>
    mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range = c(0, 1), to = c(0.5, 1)), datawizard::rescale(x, range = c(1, 0), to = c(0, 0.5))))

  # Significance
  param <- parameters::parameters(m_real, effects = "fixed", keep = var)
  sig <- data.frame(
    x = 0.5,
    y = y_real[c(11, 32), "Predicted"] + c(0.05, -0.05),
    p = c(min(param$p[c(1, 3)]), min(param$p[c(2, 4)])),
    Sex = c("Female", "Male")
  )
  sig$label <- format_p(sig$p, stars_only = TRUE)

  # Plot
  p <- df |>
    ggplot(aes_string(x = var, y = "Real")) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
    scale_fill_gradientn(colors = c("white", fill), guide = "none") +
    ggnewscale::new_scale_fill() +
    geom_hline(yintercept = 0.5, linetype = "dotted") +
    # geom_point2(alpha = 0.25, size = 4, color = "black") +
    geom_line(data = y_conf, aes(y = Predicted, group = interaction(Belief, Sex), color = Sex), linetype = "dashed") +
    geom_ribbon(data = y_real, aes(y = Predicted, group = Sex, fill = Sex, ymin = CI_low, ymax = CI_high), alpha = 1 / 3) +
    geom_line(data = y_real, aes(y = Predicted, color = Sex), size=1) +
    # geom_ribbon(data = trend, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 1/6) +
    # geom_line(data = trend, aes(y = Predicted, color=Sex, linetype=Trend, group=interaction(Sex, group)), size=0.6) +
    geom_text(data = sig, aes(y = y, x = x, label = label, color = Sex), size = 8) +
    scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
    scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
    guides(fill = guide_legend(override.aes = list(alpha = 1))) +
    theme_modern(axis.title.space = 5) +
    ggside::geom_xsidedensity(fill = fill, color = "white") +
    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))

  list(p = p, model_belief = m_real, model_confidence = m_conf)
}
```

```{r message=FALSE, warning=FALSE}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Attractive, 2) + (1|Participant) + (1|Stimulus)",
  var = "Attractive", fill = "#F44336"
)
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Beauty, 2) + Trustworthy + (1|Participant) + (1|Stimulus)",
  var = "Beauty", fill = "#E91E63"
)
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Trustworthy, 2) + Beauty + (1|Participant) + (1|Stimulus)",
  var = "Trustworthy", fill = "#4CAF50"
)
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Familiar, 2) + (1|Participant) + (1|Stimulus)",
  var = "Familiar", fill = "#2196F3"
)

(rez_at$p +
  theme(axis.text.x = element_blank()) +
  labs(x = "Attractiveness") |
  rez_gl$p +
    labs(x = "Beauty") +
    theme(
      axis.text.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
) /
  (rez_tr$p +
    labs(x = "Trustworthiness") |
    rez_fa$p +
      labs(x = "Familiarity") +
      theme(
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
      )
  ) +
  plot_annotation(title = "Determinants of Reality Beliefs", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5))) +
  plot_layout(guides = "collect")
```

```{r message=FALSE, warning=FALSE}
parameters::parameters(rez_at$model_belief, effects = "fixed", keep = "Attractive")
performance::r2(rez_at$model_belief)
performance::icc(rez_at$model_belief, by_group = TRUE)
parameters::parameters(rez_at$model_confidence, effects = "fixed", keep = "Attractive")

parameters::parameters(rez_gl$model_belief, effects = "fixed", keep = "Beauty")
performance::r2(rez_gl$model_belief)
performance::icc(rez_gl$model_belief, by_group = TRUE)
parameters::parameters(rez_gl$model_confidence, effects = "fixed", keep = "Beauty")

parameters::parameters(rez_tr$model_belief, effects = "fixed", keep = "Trustworthy")
performance::r2(rez_tr$model_belief)
performance::icc(rez_tr$model_belief, by_group = TRUE)
parameters::parameters(rez_tr$model_confidence, effects = "fixed", keep = "Trustworthy")

parameters::parameters(rez_fa$model_belief, effects = "fixed", keep = "Familiar")
performance::r2(rez_fa$model_belief)
performance::icc(rez_fa$model_belief, by_group = TRUE)
parameters::parameters(rez_fa$model_confidence, effects = "fixed", keep = "Familiar")
```
